A flexible integer linear programming formulation for scheduling clinician on-call service in hospitals

### 2020-07-06 paper/paper.comparison.tex
SM edits to comparison section

In recent years, there has been a substantial amount of literature published in
the nurse rostering area aiming to organize the types of problems and approaches
commonly
addressed in the real-world. This research serves to highlight the similarities
and differences
among computationally easy and hard instances of nurse rostering and evaluating
which algorithms
are best geared towards which types of problems thus allowing practitioners
to choose which approach will work best for their case.

De Causmaecker and Berghe [ref] outline a categorization
of nurse rostering problems using a similar approach used in theoretic scheduling problems,
based around the machine environment, job characteristics and constraints,
and optimization objective. Previously, there was a lack of a central categorization system
for nurse rostering problems found in the literature. Their work attempts
to address this by creating a classification that takes into account
hard and soft constraints related to nurse preferences, consecutive 
assignments, coverage and various flexibilities in terms of shift and
skill types. They go on to describe where recent examples of the nurse rostering
literature can fit in their classification.

>>>>

Prior work by [authors] have   %avoid editorial type statements without citations or numbers, best to state as objective statements
provided categories to organize the types of problems and approaches
commonly used for real-world nurse rostering.
These categories highlight the similarities  %SM what does "this" refer to? this paper or the prior literature? [always use a concrete noun after "this or these" to help the reader :)
and differences
among computationally easy and hard instances of nurse rostering and 
help end-users determine
which algorithms
are best suited to each type of problem.

De Causmaecker and Berghe [ref] outline a categorization
of nurse rostering problems using a similar approach used in theoretic scheduling problems,
based around the machine environment, job characteristics and constraints,
and optimization objective. Previously, there was a lack of a central categorization system
for nurse rostering problems found in the literature. Their work attempts
to address this by creating a classification that takes into account
hard and soft constraints related to nurse preferences, consecutive 
assignments, coverage and various flexibilities in terms of shift and
skill types. De Causmaecker and Berghe go on to describe where recent examples of the nurse rostering
literature can fit in their classification. %SM: such as?
